### 2022-12-06 rough_analysis.Rmd
small typos, needs relook

```{r}
#drive home a comparision in means to signify a difference in mean values.
n_means <- aov(SalePrice ~ Neighborhood, data = a1_set)
mean_diff <- TukeyHSD(n_means, conf.level = 0.95)
mean_diff
fit <- lm(SalePrice ~ Neighborhood, data = a1_set)
```

>>>>

```{r}
#drive home a comparision in means to signify a difference in mean values.
n_means <- aov(SalePrice ~ Neighborhood, data = a1_set)
mean_diff <- TukeyHSD(n_means, conf.level = 0.95)
mean_diff
fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
```
